\section{Preliminary Definitions}

\subsection{Categories}
\begin{definition}[Category]
    A category $\A$ consists of 
    \begin{enumerate}
        \item a collection $\ob(\A)$ of objects 
        \item for each $A,B\in\ob(\A)$ a collection $\A(A,B)$ of morphisms from $A$ to $B$ 
        \item for each $A,B,C\in\ob(\A)$, a composition function 
        \begin{equation*}
            \circ: \A(B,C)\times\A(A,B)\to\A(A,C)
        \end{equation*}
        mapping $(g,f)\mapsto g\circ f$.
        \item for each $A\in\ob(\A)$, an element $\id_A$ of $\A(A,A)$ called the identity on $A$.
    \end{enumerate}

    \noindent satisfying the following: 
    \begin{description}
        \item[associativity:] for each $f\in\A(A,B)$, $g\in\A(B,C)$ and $h\in\A(C,D)$, we have $(h\circ g)\circ f = h\circ (g\circ f)$
        \item[identity:] for each $f\in\A(A,B)$, we have $f\circ\id_A = f = \id_B\circ f$
    \end{description}

    Every category $\A$ also has the associated \textit{opposite category} $\A^\op$ where $\ob(\A) = \ob(\A^\op)$ and for each $A,B\in\ob(\A)$, $\A^\op(A,B) = \A(B,A)$.
\end{definition}

For example, $\catSet$ is the category of sets with morphisms as set maps.

\begin{definition}[Product Category]
    For every pair of categories $\A$ and $\B$, there is the product category $\A\times\B$ where 
    \begin{enumerate}[label=(\alph*)]
    \item $\ob(\A\times\B) = \ob(\A)\times\ob(\B)$
    \item $(\A\times\B)((A_1,B_1), (A_2,B_2)) = \A(A_1,A_2)\times\B(B_1,B_2)$ for all $A_1,A_2\in\A$ and $B_1,B_2\in\B$
    \item For $(f_1,g_1)\in(\A\times\B)((A_1,B_1), (A_2,B_2))$ and $(f_2,g_2)\in(\A\times\B)((A_2,B_2), (A_3,B_3))$, $(f_2,g_2)\circ(f_1,g_1) = (f_2\circ f_1, g_2\circ g_1)$
    \item $\mathbf{id}_{(A,B)} = (\mathbf{id}_A,\mathbf{id}_B)$ for all $(A,B)\in\A\times\B$
    \end{enumerate}
\end{definition}

\begin{definition}[Isomorphism]
    A morphism $f\in\mathscr A(A,B)$ is said to be an \textit{isomorphism} if there is $g\in\mathscr A(B,A)$ such that $g\circ f = \mathbf{id}_A$ and $f\circ g = \mathbf{id}_B$.
\end{definition}

An isomorphism in $\catSet$ is simply a bijection while an isomorphism in $\catTop$ is a homeomorphism.

\begin{definition}[Small, Locally Small]
    A category $\mathscr A$ is said to be \textit{small} $\ob(\mathscr A)$ is a set and $\mathscr A(A,B)$ is a set for all $A,B\in\mathscr A$. Similarly, $\mathscr A$ is said to be locally small if $\mathscr A(A,B)$ is a set for all $A,B\in\mathscr A$.
\end{definition}

\begin{definition}[Mono, Epi]
    In a category $\mathscr A$, an arrow $f: A\to B$ is called a/an: 
    \begin{description}
    \item[mono] if for any $C\in\mathscr A$ given any $g,h: C\to A$, $f\circ g = f\circ h$ implies $g = h$
    \item[epi] if for any $C\in\mathscr A$ given any $g,h: B\to C$, $g\circ f = h\circ f$ implies $g = h$
    \end{description}
\end{definition}

It is important to note that $\text{mono} + \text{epi}\ne\text{iso}$. For example, let $\mathbf P$ be a poset category. Then, every arrow $p\le q$ is a mono and an epi but not all arrows are isos. Similarly, in $\catCRing$, the inclusion $\iota:\Z\hookrightarrow\Q$ is a mono and an epi but not an iso.

\begin{proposition}
    Epis in $\catGrp$ are precisely surjective group homomorphisms.
\end{proposition}
\begin{proof}
\end{proof}

\begin{definition}[Initial, Terminal]
    In a category $\A$, an object $\mathbf 0$ is said to be \textit{initial} if for each $A\in\A$, $\mathscr A(\mathbf 0,A)$ is a singleton. Similarly, an object $\mathbf 1$ is said to be \textit{terminal} if for each $A\in\A$, $\A(A,\mathbf 1)$ is a singleton.
\end{definition}

In $\catSet$, the empty set is the initial object while every singleton is a terminal object. In $\catCRing$, $\Z$ is an initial object while the zero ring is a terminal object.

\begin{proposition}
    Initial (terminal) objects are unique upto a unique isomorphism.
\end{proposition}
\begin{proof}
    Let $\mathbf 0$ and $\mathbf 0'$ be initial objects in $\A$. Then, there are unique morphisms $f:\mathbf 0\to\mathbf 0'$ and $g:\mathbf 0\to\mathbf 0'$. Since $g\circ f\in\A(\mathbf 0,\mathbf 0')$, we must have $g\circ f = \mathbf{id}_{\mathbf 0}$ and similarly, $f\circ g = \mathbf{id}_{\mathbf 0'}$. Hence $f$ and $g$ are isomorphisms. Uniqueness follows from the definition of initial objects.

    An analogous proof works for terminal objects.
\end{proof}


\subsection{Functors}

\begin{definition}[Functor]
    Let $\A$ and $\B$ be categories. A functor $F:\A\to\B$ consists of 
    \begin{itemize}
        \item a function $\ob(\A)\to\ob(B)$ written as $A\mapsto F(A)$
        \item for each $A,A'\in\A$, a function $\A(A,A')\to\B(F(A),F(A'))$, written as $f\mapsto F(f)$
    \end{itemize}

    \noindent satisfying the following axioms
    \begin{description}
        \item[covariancy:] $F(f'\circ f) = F(f')\circ F(f)$ whenever $A\stackrel{f}{\longrightarrow} A'\stackrel{f'}{\longrightarrow}A''$ in $\A$ 
        \item[identity consistency:] $F(\id_A) = \id_{F(A)}$ whenever $A\in\A$ 
    \end{description}

    Such a functor is sometimes also called a \textbf{covariant functor}.
\end{definition}

Let $\catTop_*$ denote the category of topological spaces equipped with a basepoint. Let $\pi$ be the map that maps a pointed topological space $(X,x_0)$ to its fundamental group $\pi(X,x_0)$. We claim that this is a covariant functor. Let $\phi: (X,x_0)\to(Y,y_0)$ be a continuous function. One knows from algebraic topology that the above continuous map induces a homomorphism $\phi_*:\pi(X,x_0)\to\pi(Y,y_0)$ given by $[f]\mapsto[\phi\circ f]$. It is not hard to see that this is a covariant functor.

\begin{definition}[Contravariant Functor]
    Let $\A$ and $\B$ be categories. A contravariant functor from $\A$ to $\B$ is a functor $F:\A^\op\to\B$.
\end{definition}

Let $\catTop$ be the category of topological spaces. For a topological space $X$, let $C(X)$ denote the ring of continuous functions $X\to\R$. That is, $C(X)\in\catRing$. We claim that $C(X)$ is a contravariant functor from $\catTop$ to $\catRing$. Indeed, let $f: X\to Y$ be a continuous function. Then, we have the following commutative diagram: 
\begin{equation*}
\xymatrix {
    X\ar[r]^f\ar[rd]_{g\circ f} & Y\ar[d]^g\\
    & \R
}
\end{equation*}

The continuous function $f$ induces a map $f_*: C(Y)\to C(X)$ given by $g\mapsto g\circ f$. It is not hard to see now that the functor $C$ is a contravariant functor from $\catTop$ to $\catRing$ which maps a morphism $f$ to a morphism $f_*$.


\begin{definition}[Presheaf]
    A presheaf is a contravariant functor from $\mathscr A$ to $\catSet$. That is, a functor $F:\A^\op\to\catSet$.
\end{definition}

Let $X$ be a topological space and let $\mathscr O(X)$ denote the category of open subsets of $X$ with inclusion morphisms. This gives $\mathscr O(X)$ the structure of a poset. Consider now the map $F:\mathscr O(X)^\op\to\catSet$ given by 
\begin{equation*}
    F(U) = \left\{\text{continuous functions }U\to\R\right\}
\end{equation*}
That this is a functor follows from the fact that if $U\subseteq V$, then the restriction of a continuous function $f: V\to\R$ to $U$ is continuous.

\begin{definition}
    A functor $F:\mathscr A\to\mathscr B$ is \textit{faithful} if for each $A,A'\in\mathscr A$, the map $\mathscr A(A,A')\to\mathscr B(F(A),F(A'))$ given by $f\mapsto F(f)$ is injective.

    Similarly, it is said to be \textit{full} if the map is surjective.
\end{definition}

\subsection{Natural Transformations}

\begin{definition}[Natural Transformation]
    Let $\mathscr A$ and $\mathscr B$ be categories and let $F, G:\mathscr A\longrightarrow\mathscr B$ be functors. A \textit{natural transformation} $\alpha: F\to G$ is a family $\left(F(A)\stackrel{\eta_A}{\longrightarrow}G(A)\right)_{A\in\mathscr A}$ of maps in $\mathscr B$ such that for every map $A\stackrel{f}{\longrightarrow}A'$ in $\mathscr A$, the following diagram commutes
    \begin{equation*}
        \xymatrix{
            F(A)\ar[r]^{F(f)}\ar[d]_{\eta_A} & F(A')\ar[d]^{\eta_{A'}}\\
            G(A)\ar[r]_{G(f)} & G(A')
        }
    \end{equation*}
    The maps $\eta_A$ are called the \textit{components} of $\eta$. When $\eta_A$ is an isomorphism for all $A\in\mathscr A$, then $\eta$ is said to be a natural isomorphism.
\end{definition}

Consider $\catCRing$, the category of commutative rings and $\catMon$, the category of monoids. Consider the covariant functor $M_n:\catCRing\to\catMon$ that maps a commutative ring $R$ to the monoid $M_n(R)$ of $n\times n$ matrices with entries from $R$. 

Consider now the forgetful functor $U:\catCRing\to\catMon$ that maps a ring $R$ to its multiplicative monoid. It is not hard to see that $\det_n$ is a natural transformation from $M_n\to U$.