\begin{definition}[Covering Space]
    A covering space of a space $X$ is a space $\widetilde X$ together with a map $p:\widetilde X\to X$ satisfying the condition that there is an open cover $\{U_\alpha\}$ of $X$ such that for each $\alpha\in J$, $p^{-1}(U_\alpha)$ is a disjoint union of open sets in $\widetilde X$, each of which is mapped homeomorphically by $p$ to $U_\alpha$.
\end{definition}

Notice that for each $x\in X$, the subspace $p^{-1}(x)$ of $\wt X$ has the discrete topology. 

\begin{proposition}
    Let $p:\wt X\to X$ be a covering map where $X$ is connected. If for some $x\in X$, $|p^{-1}(x)| = n\in\N$, then for all $x'\in X$, $|p^{-1}(x')| = n$.
\end{proposition}
\begin{proof}
    The map $x\mapsto|p^{-1}(x)|$ is locally constant and thus continuous. Owing to $X$ being connected and $\N$ having the discrete topology, the aforementioned map must be constant.
\end{proof}

\section{Lifting Properties}

\begin{definition}[Lift]
    Let $f: Y\to X$ be a continuous and $p:\widetilde X\to X$ be a covering map. A \textit{lift} of $f$ is a map $\widetilde f: Y\to\widetilde X$ such that $f = p\circ\widetilde f$. 
    \begin{equation*}
        \xymatrix{
            & {\widetilde X}\ar[d]^p\\
            Y\ar[r]_f\ar[ru]^{\widetilde f} & X
        }
    \end{equation*}
\end{definition}

\begin{theorem}\thlabel{thm:unique-lifting-connected}
    Let $Y$ be connected and $p:\widetilde X\to X$ a covering map. If $f: Y\to X$ is a continuous map having two lifts $\widetilde f_1,\widetilde f_2: Y\to\widetilde X$, that agree at some point in $Y$, then they agree on all of $Y$.
\end{theorem}
\begin{proof}
    Let 
    \begin{equation*}
        A = \{y\in Y\mid \widetilde f_1(y) = \widetilde f_2(y)\}
    \end{equation*}
    We shall show that $A$ is clopen in $Y$, whence we would be done owing to $A$ being nonempty. Let $y\in A$ and $x = f(y)$. There is a neighborhood $U$ of $x$ such that $p^{-1}(U)$ is a disjoint union of $\{V_\alpha\}$ which are homeomorphically mapped to $U$. Let $V_\beta$ be the one containing $\widetilde x = \widetilde f_1(y) = \widetilde f_2(y)$. Then, due to continuity, there is a neighborhood $N$ of $y$ that is mapped into $V_\beta$ by both $\widetilde f_1$ and $\widetilde f_2$. Then, for all $z\in N$, $p\circ\widetilde f_1(z) = p\circ\widetilde f_2(z)$ but since $p$ is injective on $V_\beta$, we must have $\widetilde f_1(z) = \widetilde f_2(z)$, consequently, $N\subseteq A$ and $A$ is open.

    On the other hand, if $y\notin A$, then $\widetilde f_1(y)$ and $\widetilde f_2(y)$ lie in distinct open sets $V_{\beta_1}$ and $V_{\beta_2}$, consequently, for all $z\in N = \widetilde f_1^{-1}(V_{\beta_1})\cap\widetilde f_2^{-1}(V_{\beta_2})$, $\widetilde f_1(z)\ne\widetilde f_2(z)$, thereby completing the proof.
\end{proof}

\begin{theorem}[Homotopy Lifting Property]\thlabel{thm:homotopy-lifting}
    Let $p:\widetilde X\to X$ be a covering map and $F: Y\times I\to X$ a continuous map. Let $\widetilde F_0: Y\to\widetilde X$ be a lift of $F|_{X\times\{0\}}$. Then, there is a unique lift $\widetilde F: Y\times I\to\widetilde X$ of $F$ such that $\widetilde F|_{X\times\{0\}} = \widetilde F_0$.
\end{theorem}
\begin{proof}
    The first step is to define a lift $\wt F$ on the strip $N\times I$ where $N$ is a neighborhood of some point $y\in Y$. 

    Fix some $y_0\in Y$. Each point $y_0\times t$ has a neighborhood $N_t\times(a_t,b_t)$ which maps maps into an evenly covered neighborhood of $F(y_0\times t)$. Note that the strip $\{y_0\}\times I$ is compact and is thus covered by finitely many of the $N_t$'s, whence we may choose a neighborhood $N$ of $y_0$ in $Y$ and a partition $0 = t_0 < t_1 < \dots < t_n = 1$ such that each $N\times [t_i, t_{i + 1}]$ is contained in $N_t\times(a_t,b_t)$ for some $t\in I$.

    Now suppose $\wt F$ has been constructed on $N\times[0,t_i]$. We already have a lift for $N\times\{0\}$ and this is our base case. The space $N\times[t_i, t_{i + 1}]$ is mapped into an evenly covered neighborhood $U$ by $F$. Let $\wt U\subseteq\wt X$ be the unique open set in $\wt X$ containing the point $\wt F(y_0\times t_i)$. There is a neighborhood $N'$ of $y_0$ such that $N'\times\{t_i\}$ is mapped into $\wt U$ by $\wt F$. Replace $N$ by $N'$ henceforth. The composition $p^{-1}\circ F$ now lifts $F$ on $N'\times[t_i, t_{i + 1}]$ and since it agrees with $\wt F$ on $N'\times\{t_i\}$, we have an extension to $\wt F$ on $N\times[0, t_{i + 1}]$, which is continuous due to the Pasting Lemma.

    Now, for each $y\in Y$, we have constructed a lift $\wt F_y$ on $N_y\times I$ where $N_y$ is some neighborhood of $y$. We must now argue that we can indeed paste these lifts together. Let $y\in N_{y'}\cap N_{y''}$. Since $\{y\}\times I$ is connected and $\wt F_{y'}$ and $\wt F_{y''}$ are two lifts which agree at $y\times 0\in\{y\}\times I$, both the lifts must agree throughout due to \thref{thm:unique-lifting-connected}. This also establishes the uniqueness of the lift $\wt F$ whereby completing the proof.
\end{proof}

\begin{corollary}[Path Lifting]\thlabel{corr:path-lifting}
    Let $f: I\to X$ be a path and let $x_0 = f(0)$. For any $\widetilde x_0\in p^{-1}(x_0)$, there is a unique lift $\widetilde f: I\to\widetilde X$ such that $\widetilde f(0) = \widetilde x_0$.
\end{corollary}

\begin{corollary}[Path Homotopy Lifting]\thlabel{corr:path-homotopy-lifting}
    Let $H: I\times I\to X$ be a path homotopy. Then, the unique lift $\wt H: I\times I\to\wt X$, is also a path homotopy.
\end{corollary}
\begin{proof}
    Since the image $\wt H(\{0\}\times I)$ is connected and a subset of the discrete fiber of $p^{-1}(\wt H(0\times 0))$, it must be a single point. Similarly argue for the image $\wt H(\{1\}\times I)$. This completes the proof.
\end{proof}

\begin{proposition}\thlabel{prop:induced-covering-injective}
    Let $p:(\widetilde X,\widetilde x_0)\to(X,x_0)$ be a covering map. Then the induced homomorphism $p_*:\pi_1(\widetilde X,\widetilde x_0)\to\pi_1(X,x_0)$ is injective.
\end{proposition}
\begin{proof}
    It suffices to show that $\ker p_*$ is trivial. Indeed, let $f: I\to\wt X$ be such that $p_*([f]) = 1_{\pi_1(X,x_0)}$. Thus, there is a path homotopy $F: I\times I\to X$ such that $F|_{I\times\{1\}}$ is the constant map at $x_0$ while $F|_{I\times\{0\}}$ is the map $p\circ f$.
    \begin{equation*}
        \xymatrix {
            & \wt X\ar[d]^{p}\\
            I\times I\ar[r]_-{F}\ar[ru]^-{\wt F} & X
        }
    \end{equation*}
    We have a lift $\wt F: I\times\{0\}\to\wt X$ of the bottom edge given by $\wt F(t\times 0) = f(t)$ and due to \thref{thm:homotopy-lifting}, this can be extended to a lift $\wt F: I\times I\to\wt X$. Consider the connected subspace $Y = \{0\}\times I\cup I\times\{1\}\cup\{1\}\times I$ of $I\times I$. The restriction $\wt F|_{Y}$ maps into $p^{-1}(x_0)$, which has the discrete topology, whereby the restriction must be a constant map equal to $\wt x_0$ since $\wt F(0\times 0) = \wt x_0$. Thus, $\wt F$ must be a path homotopy between $f$ and the constant path $\wt x_0$, thereby completing the proof.
\end{proof}

\begin{proposition}
    Let $\wt X$ and $X$ be path connected spaces with a covering map $p:(\wt X, \wt x_0)\to(X,x_0)$. Then, there is a bijection between the right cosets of $H = p_*(\pi_1(\wt X, \wt x_0))$ and $p^{-1}(x_0)$.
\end{proposition}
\begin{proof}
    \todo{right coset to $p^{-1}$ bijection}
\end{proof}

\begin{theorem}[Lifting Criterion]\thlabel{thm:lifting-criterion}
    Let $Y$ be path connected and locally path connected and $p:(\widetilde X,\widetilde x_0)\to(X,x_0)$ be a covering map. Then, for any continuous map $f:(Y,y_0)\to(X,x_0)$, a lift $\widetilde{f}:(Y,y_0)\to(\widetilde X,\widetilde x_0)$ exists if and only if $f_*(\pi_1(Y,y_0))\subseteq p_*(\pi_1(\widetilde X,\widetilde x_0))$.
\end{theorem}
\begin{proof}
    The forward direction is trivial, we shall prove the converse. Let $y\in Y$ and $\gamma$ denote a path from $y_0$ to $y$ in $Y$. The image $f\circ\gamma$ is a path in $X$ beginning at $x_0$ and has a lift $\wt{f\circ\gamma}$ to a path in $\wt X$ beginning at $\wt x_0$. Define the map $\wt f: Y\to\wt X$ by $\wt f(y) = \wt{f\circ\gamma}(1)$. 

    First, we must show that this is a well defined map, independent of the choice of $\gamma$. Indeed, let $\gamma'$ be another path in $Y$ from $y_0$ to $y$. Then, $\gamma'\ast\overline\gamma$ is a loop in $\gamma'$ based at $y_0$, whence $f\circ(\gamma'\ast\overline\gamma)$ is a loop in $X$ based at $x_0$. We must now show that this can be lifted to a \emph{loop}\footnote{We can always lift this to a path but that will not suffice in this case} in $\wt X$ based at $\wt x_0$. 

    According to our hypothesis, $\left[{f\circ\gamma'} * \overline{{f\circ\gamma}}\right]\in p_\ast(\pi_1(\wt X,\wt x_0))$ whence there is a path homotopy $H: I\times I\to X$ between $p\circ\wt h$ and ${f\circ\gamma'} * \overline{{f\circ\gamma}}$ where $\wt h$ is a loop in $\wt X$. Due to \thref{corr:path-homotopy-lifting}, this lifts to a homotpy of paths in $\wt X$. Due to the uniqueness of path lifting, $\wt H$ is a path homotopy between the loop $\wt h$ and some other loop $\wt\alpha$ in $\wt X$ that maps to ${f\circ\gamma'} * \overline{{f\circ\gamma}}$ under $p$. 

    Considering the first and second halves of $\wt\alpha$, we see that they are $\wt{f\circ\gamma'}$ and $\overline{\wt{f\circ\gamma'}}$ respectively. Therefore, $\wt{f\circ\gamma'}(1) = \wt{f\circ\gamma}(1)$ and the map $\wt f$ is well defined.

    Finally, we must show that $\wt f$ is continuous. Let $y\in Y$ and $U\subseteq X$ be an evenly covered open neighborhood of $f(y)$. Choose an open path connected neighborhood $V$ of $y$ that is contained in $p^{-1}(U)$. Let $\wt U$ be the open set in $\wt X$ that is homeomorphically mapped to $U$ by $p$ and contains $\wt f(y)$. We shall show that $\wt f(V)\subseteq\wt U$, which would imply $\wt f|_V = p^{-1}\circ f$, thereby implying local continuity and thus the continuity of $\wt f$.

    First, fix some path $\gamma$ from $y_0$ to $y$ in $Y$. Let $y'\in V$ and choose some path $\eta$ from $y$ to $y'$ contained in $V$. The path $\gamma\ast\eta$ is a path from $y_0$ to $y'$. The composition $p^{-1}\circ\eta$ is a path from $\wt f(y)$ in $\wt U$, moreover, the composition $\wt{f\circ\gamma} * p^{-1}\circ\eta$ is a path from $\wt x_0$ lifting $\gamma*\eta$, whence $p^{-1}\circ\eta(1) = \wt f(1)$ and $\wt f(V)\subseteq\wt U$. This completes the proof.
\end{proof}


\section{The Universal Cover}

\begin{definition}[Semilocally Simply-Connected]
    A topological space $X$ is said to be \textit{semilocally simply-connected} if each point $x\in X$ has a neighborhood $U$ such that the inclusion induced homomorphism $i_*:\pi(U, x)\to\pi(X,x)$ is trivial.
\end{definition}

Henceforth, a topological space is said to be \nice if it is path-connected, locally path-connected and semilocally simply-connected.

\begin{theorem}\thlabel{thm:universal-cover-exists}
    If $X$ is \nice, then there is a simply connected space $\widetilde X$ and a covering map $p:\widetilde X\to X$.
\end{theorem}
\begin{proof}
Pick a basepoint $x_0\in X$. Define
\begin{equation*}
    \widetilde X = \{[\gamma]\mid\gamma: I\to X,~\gamma(0) = x_0\}
\end{equation*}
and the function $p:\widetilde X\to X$ by $p([\gamma]) = \gamma(1)$.

Let $\mathscr U$ denote the set of all path connected open sets $U\subseteq X$ such that the homomorphism induced by the inclusion $U\hookrightarrow X$ is trivial. Indeed, if $V\subseteq U\in\mathscr U$ is path connected and open, then the homomorphism induced by the inclusion $V\hookrightarrow X$ is the composition of the homomorphisms induced by $V\hookrightarrow U\hookrightarrow X$ and since the latter is trivial, the composition is trivial, consequently, $V\in\mathscr U$.

We contend that $\mathscr U$ forms a basis for the topology on $X$. Indeed, let $W$ be a neighborhood of $x$, then there is a neighhborhood $U$ of $x$ such that the homomorphism induced by the inclusion $U\hookrightarrow X$ is trivial. Since $X$ is locally path connected, there is a path connected neighborhood $V$ of $x$ that is contained in $U\cap W$, whence the conclusion follows.

We shall now topologize $\widetilde{X}$. Let $\gamma$ be a path in $X$ from $x_0$ and $U\in\mathscr U$ contain $\gamma(1)$. Define the set 
\begin{equation*}
    U_{[\gamma]} = \left\{[\gamma * \eta]\mid \eta: I\to U,~\eta(0) = \gamma(1)\right\}
\end{equation*}
where the equivalence classes are in $X$. Since $U$ is path connected, $p: U_{[\gamma]}\to U$ is surjective. Moreover, since the homomorphism induced by the inclusion $U\hookrightarrow X$ is trivial, any two paths from $\gamma(1)$ to any point $x\in U$ are homotopic in $X$.

We contend that if $[\gamma']\in U_{[\gamma]}$, then $U_{[\gamma']} = U_{[\gamma]}$. Obviously, there is a path $\eta: I\to U$ such that $\gamma' = \gamma * \eta$, whence it follows that $\gamma' * \mu = \gamma * \eta * \mu$ and thus, $U_{[\gamma']}\subseteq U_{[\gamma]}$. On the other hand, $[\gamma * \mu] = [\gamma * \eta * \overline{\eta} * \mu]$ whereby the conclusion follows.

Next, we claim that the collection $\{U_{\gamma}\}$ forms a basis for a topology on $\widetilde X$. Suppose $[\gamma'']\in U_{[\gamma]}\cap V_{[\gamma']}$ where $U,V\in\mathscr U$, then $U_{[\gamma]} = U_{[\gamma'']}$ and $V_{[\gamma']} = V_{[\gamma'']}$. Since $\mathscr U$ forms a basis, there is $W\in\mathscr U$ such that $W\subseteq U\cap V$, consequently, $W_{[\gamma'']}\subseteq U_{[\gamma'']}\cap V_{[\gamma'']}$. This proves our claim.

Consider the bijection $p: U_{[\gamma]}\to U$, we contend that this is a homeomorphism. For any basis element $V_{[\gamma']}\subseteq U_{[\gamma]}$, we have $p(V_{[\gamma']}) = V$, consequently, $p$ is an open map. On the other hand, if $V\subseteq U$ is an open set, then $p^{-1}(V)\cap U_{[\gamma]} = V_{[\gamma']}$ for some $[\gamma']\in U_{[\gamma]}$ with $\gamma'(1)\in V$. Since $V_{[\gamma']}\subseteq U_{[\gamma']} = U_{[\gamma]}$, we see that the restriction of $p$ is continuous and therefore a homeomorphism.

Using the local formulation of continuity, we have that $p:\widetilde X\to X$ is a continuous map. Any $x\in X$ has a neighborhood $U\in\mathscr U$, consequently, $p^{-1}(U) = \bigcup U_{[\gamma]}$ where $[\gamma]$ ranges over all paths from $x_0$ to some point in $U$. It is not hard to argue that the sets $U_{[\gamma]}$ must partition $p^{-1}(U)$, whereby $p$ is a covering map.

Finally, we must show that $\widetilde X$ is simply connected. Pick the base point $[x_0]\in\widetilde{X}$. First, we show that $\widetilde X$ is path connected. Let $[\gamma]\in\widetilde X$. Define $\gamma_t: I\to X$ by 
\begin{equation*}
    \gamma_t(s) = 
    \begin{cases}
        \gamma(s) & 0\le s\le t\\
        \gamma(t) & t < s \le 1
    \end{cases}
\end{equation*}
It suffices to show that the map $\varphi: I\to\widetilde X$ given by $\varphi(t) = [\gamma_t]$ is continuous. Using the Lebesgue Number Lemma, there is a partition $0 = t_0 < t_1 < \cdots < t_n = 1$ such that $\gamma([t_{i - 1}, t_i])\subseteq U_i\in\mathscr U$. Let $p_i: U_{i[\gamma_{t_i}]}\to U_i$ be the restriction of $p$, which is a homeomorphism. Then, for all $t\in[t_{i - 1}, t_i]$, $\varphi(t) = p_i^{-1}(\gamma(t))$ and continuity follows from the Pasting Lemma.

Next, we show $\pi_1(\widetilde X,[x_0]) = 0$. Since $p_*$ is injective, it suffices to show that the image of $p_*$ is trivial. Let $\gamma$ be a loop in the image of $p_*$. Then, the map $t\mapsto[\gamma_t]$ is a lift of $\gamma$ as we have seen earlier and is unique due to \thref{thm:homotopy-lifting}. Now, since the lift is a loop, we must have 
\begin{equation*}
    [x_0] = [\gamma_1] = [\gamma]
\end{equation*}
consequently, $\gamma$ is nulhomotopic. This completes the proof.
\end{proof}

\begin{theorem}
    Suppose $X$ is \nice. Then for every subgroup $H\subseteq\pi_1(X,x_0)$, there is a covering space $p: (X_H,\widetilde x_0)\to (X,x_0)$  such that $p_*(\pi_1(X_H,\widetilde{x}_0)) = H$.
\end{theorem}
\begin{proof}
    For $[\gamma],[\gamma']\in\wt X$, define the relation $[\gamma]\sim_H[\gamma']$ to mean $\gamma(1) = \gamma'(1)$ and $[\gamma\ast\overline{\gamma'}]\in H$. This is obviously an equivalence relation. Let $X_H$ denote the quotient space $X/\sim_H$ with $q:\wt X\to X_H$ the quotient map. Consider now the map $p: X_H\to X$ which is induced as shown in the following diagram. 
    \begin{equation*}
        \xymatrix {
            \wt X \ar@{->>}[r]^\pi\ar@{->>}[d]_q & X\\
            X_H\ar@{.>}[ru]_{\exists! p}
        }
    \end{equation*}

    Let $U\subseteq X$ be an open neighborhood. Then, $p^{-1}(U)$ is a disjoint union $\bigsqcup U_{[\gamma]}$ where $[\gamma]$ is an equivalence class of paths with $\gamma(1)\in U$. Note that $[\gamma]\sim_H[\gamma']$ if and only if $[\gamma\ast\eta]\sim_H[\gamma'\ast\eta]$. Hence, if any two points in distinct neighborhoods $U_{[\gamma]}$ and $U_{[\gamma']}$ are identified, then so are the entire neighborhoods. Hence, $p: X_H\to X$ is a covering map.

    Choose the basepoint $\wt x_0\in X_H$ the equivalence class under $\sim_H$ containing the point $[e_{x_0}]$ where $e_{x_0}$ is the constant path at $x_0$. Let $\gamma$ be a loop in $X$ based at $x_0$. This lifts to a path from $[e_{x_0}]$ to $[\gamma]$ in $\wt X$. This lift maps to a loop in $X_H$ if and only if $[e_{x_0}]\sim_H[\gamma]$ or equivalently, $[\gamma]\in H$. In particular, this means that $p_\ast(\pi_1(X_H, \wt x_0)) = H$. This completes the proof.
\end{proof}

\begin{definition}
    If $p_1: (\widetilde X_1,\widetilde x_1)\to(X,x_0)$ and $p_2:(\widetilde X_2,\widetilde x_2)\to(X,x_0)$ are covering spaces, then an \textit{isomorphism between} them is a homeomorphism $f: (\widetilde X_1,\widetilde x_1)\to(\widetilde X_2,\widetilde x_2)$ such that $p_1 = p_2\circ f$.
\end{definition}

\begin{theorem}\thlabel{thm:isomorphism-iff-image-equal}
    Let $(X, x_0)$ be \ul{path connected and locally path connected} and $p_1:\widetilde X_1\to X$ and $p_2:\widetilde X_2\to X$ be covering spaces. Then, for $\widetilde x_1\in p_1^{-1}(x_0)$ and $\widetilde x_2\in p_2^{-1}(x_0)$, there is an isomorphism $f: (\widetilde X_1,\widetilde x_1)\to(\widetilde X_2,\widetilde x_2)$ if and only if $p_{1*}(\pi_1(\widetilde X_1,\widetilde x_1)) = p_{2*}(\pi_1(\widetilde{X}_2, \widetilde x_2))$.
\end{theorem}
\begin{proof}
    We prove the converse, since the forward direction is trivial. Using \thref{thm:lifting-criterion}, there are lifts $\widetilde p_1: (\widetilde X_1,\widetilde x_1)\to(\widetilde X_2,\widetilde x_2)$ and $\wt p_2: (\wt X_2,\wt x_2)\to(\wt X_1,\wt x_1)$ of $p_1$ and $p_2$ respectively. This give us $p_1 = p_2\circ\wt p_1$ and $p_2 = p_1\circ\wt p_2$, whereby $p_1\circ(\wt p_2\circ\wt p_1) = p_1$. Note that this implies $\wt p_2\circ\wt p_1$ is a lift of the map $p_1$, but since $\mathbf{id}_{(\wt X_1,\wt x_1)}$ is also a lift, and agree on $\wt x_1$, we must have that $\wt p_2\circ\wt p_1 = \mathbf{id}_{(\wt X_1, \wt x_1)}$ and similarly, $\wt p_1\circ\wt p_2 = \mathbf{id}_{(\wt X_2,\wt x_2)}$. This implies the desired conclusion.
\end{proof}

\begin{theorem}
    Let $X$ be \ul{path connected and locally path connected}. Then, there is a bijection between the isomorphism classes of path connected covering spaces $p:\wt X\to X$  (ignoring basepoints) and conjugacy classes of subgroups of $\pi_1(X)$\footnote{The basepoint can be ignored since $X$ is path connected.}.
\end{theorem}
\begin{proof}
    Fix, once and for all, a basepoint $x_0\in X$ and let $G = \pi_1(X,x_0)$. Suppose we have an isomorphism of covering spaces (ignoring basepoints)
    \begin{equation*}
        \xymatrix {
            {\wt X_1}\ar[rr]^f\ar[rd]_{p_1} && {\wt X_2}\ar[ld]^{p_2}\\
            & X & 
        }
    \end{equation*}
    given by the above diagram with the basepoints $\wt x_1\in p_1^{-1}(x_0)$ and $\wt x_2\in p_2^{-1}(x_0)$. Then, due to the commutativity of the diagram, we have 
    \begin{equation*}
        (p_1)_\ast(\pi_1(\wt X_1,\wt x_1)) = (p_2)_\ast\circ f_\ast(\pi_1(\wt X_1, \wt x_1)) = (p_2)_\ast(\pi_1(\wt X_2, \wt x_2)).
    \end{equation*}

    We now contend that changing the basepoint in a covering space $p:\wt X\to X$ conjugates the image under $p_\ast$. Indeed, let $\wt x_0,\wt x_1\in p^{-1}(x_0)$ where $x_0$ is the chosen basepoint of $X$ and let $\wt\gamma$ be a path from $\wt x_0$ to $\wt x_1$. Let $H_i = p_\ast(\pi_1(\wt X,\wt x_i))$ and let $g = p_\ast([\wt\gamma])$.

    If $\wt f$ is a loop in $\wt X$ based at $\wt x_0$, then 
    \begin{equation*}
        g^{-1}p_\ast([\wt f])g = p_\ast([\overline{\wt\gamma} * \wt f * \wt\gamma])\in H_1
    \end{equation*}
    and thus, $g^{-1}H_0g\subseteq H_1$. Similarly, one can show that $gH_1g^{-1}\subseteq H_0$, implying that $H_0$ and $H_1$ are conjugate subgroups of $G$.

    Conversely, suppose $p_1: (\wt X_1,\wt x_1)\to(X,x_0)$ and $p_2: (\wt X_2,\wt x_2)\to(X,x_0)$ are covering maps with $H_i = (p_1)_\ast(\pi_1(\wt X_i,\wt x_i))$ and there is $g\in G$ such that $H_2 = g^{-1}H_1g$. Let $\gamma$ be a loop in the equivalence class corresponding to $g$, then this has a lift $\wt\gamma$ in $\wt X_1$ and let $\wt y_1 = \wt\gamma(1)\in p_1^{-1}(x_0)$. 

    It is not hard to see that $(p_1)_\ast(\pi_1(\wt X_1, \wt y_1)) = H_2$ whence there is a basepoint preserving isomorphism (since the covering spaces are path connected) $f:(\wt X_1,\wt y_1)\to(\wt X_2,\wt x_2)$ thereby proving the theorem.
\end{proof}

In conclusion, we have proved the following classification theorem.

\begin{theorem}\thlabel{thm:classification-covering-spaces}
    Let $X$ be \nice and $x_0\in X$ a chosen basepoint. Then there is a bijection between the set of basepoint preserving isomorphism classes of path connected covering spaces and the set of subgroups of $\pi_1(X,x_0)$. 

    On the other hand, if basepoints are ignored, then there is a bijecion between the isomorphism classes of covering spaces of $X$ and conjugacy classes of subgroups of $\pi_1(X,x_0)$.
\end{theorem}

\subsection{Action of \texorpdfstring{$\pi_1$}{fg} on a fiber}

Let $p:\wt X\to X$ be a covering map and $x_0\in X$. We shall first define an action of the group $\pi_1(X,x_0)$ on $p^{-1}(x_0)$. For a loop $\gamma$ based at $x_0$, define the function $L_\gamma: p^{-1}(x_0)\to p^{-1}(x_0)$ as follows: Choose some $\wt x_0\in p^{-1}(x_0)$ and let $\wt\gamma$ denote the \emph{unique} lift of $\gamma$ to a path in $\wt X$ that begins at $\wt x_0$. Define $L_\gamma(\wt x_0) := \wt\gamma(1)$.

First, note that $L_\gamma$ is a bijection since it has an inverse given by $L_{\overline\gamma}$. Now, suppose $\gamma$ and $\gamma'$ are path homotopic loops, that is, $[\gamma] = [\gamma']$. Choose some $\wt x_0\in p^{-1}(x_0)$. Then, due to \thref{corr:path-homotopy-lifting}, the lifts $\wt\gamma$ and $\wt{\gamma'}$ are path homotopic too, whence $\wt\gamma(1) = \wt{\gamma'}(1)$ and thus $L_{\gamma} = L_{\gamma'}$.

Finally, suppose $\gamma$ and $\eta$ are two loops based at $x_0$ and $\wt x_0\in p^{-1}(x_0)$. Let $\wt x_1 = \wt\gamma(1)$ and $\wt\eta$ be the unique lift of $\eta$ to a path in $\wt X$ beginning at $\wt x_1$. Then, $\wt\gamma\ast\wt\eta$ is the \emph{unique} lift of $\gamma\ast\eta$ to $\wt X$ whence, $L_{\gamma\ast\eta} = L_\eta\circ L_\gamma$. 

Consider now the map $\Phi:\pi_1(X,x_0)\to\mathfrak S\left(p^{-1}(x_0)\right)$ given by $[\gamma]\mapsto L_{\overline\gamma} = L_\gamma^{-1}$. Then, 
\begin{equation*}
    \Phi([\gamma]\ast[\eta]) = L_{\overline{\gamma\ast\eta}} = L_{\overline\eta\ast\overline\gamma} = L_{\overline\gamma}\circ L_{\overline\eta} = \Phi([\gamma])\circ\Phi([\eta]),
\end{equation*}
whence $\Phi$ is a group homomorphism and defines an \emph{action of $\pi_1(X,x_0)$ on the fiber $p^{-1}(x_0)$.}


\section{Deck Transformations and Covering Space Actions}

\subsection{Deck Transformations}
\begin{definition}[Deck Transformations, Normal Coverings]
    For a covering space $p:\wt X\to X$, the isomorphisms $f: X\to X$ are called \textit{deck transformations}. These form a group $G(\wt X)$ under composition. 

    A covering space $p:\wt X\to X$ is said to be \textit{normal} if for all $x\in X$ and each pair $\wt x,\wt x'\in p^{-1}(x)$, there is a deck transformation that maps $\wt x\mapsto\wt x'$.
\end{definition}

\begin{proposition}\thlabel{prop:deck-action-free}
    Let $\wt X$ be connected. Then, $G(\wt X)$ acts freely on $\wt X$. In particular, a deck transformation, in this case, is completely determined by where it sends a single point.
\end{proposition}
\begin{proof}
    Let $f\in G(\wt X)$ have a fixed point $\wt x_0$. Then, this is a lift for $p:(\wt X, \wt x_0)\to(X,x_0)$ as seen from the following diagram. 
    \begin{equation*}
        \xymatrix {
            & (\wt X, \wt x_0)\ar[d]^p\\
            (\wt X,\wt x_0)\ar[r]_p\ar[ru]^{f,\id} & (X,x_0)
        }
    \end{equation*}
    But since $f$ and $\id$ agree at $\wt x_0$, they must agree everywhere due to \thref{thm:unique-lifting-connected}.
\end{proof}

\begin{theorem}\thlabel{thm:ftgt-covering-spaces}
    Let $p: (\wt X,\wt x_0)\to(X,x_0)$ be a path-connected covering space of the \ul{path-connected, locally path-connected} space $X$, and let $H$ be the subgroup $p_*(\pi_1(\wt X,\wt x_0))$ of $\pi_1(X,x_0)$. Then, 
    \begin{enumerate}[label=(\alph*)]
        \item the covering space is normal if and only if $H$ is normal in $\pi_1(X,x_0)$ 
        \item $G(\wt X)$ is isomorphic to the quotient $N(H)/H$ where $N(H)$ is the normalizer of $H$ in $\pi_1(X,x_0)$.
    \end{enumerate}
\end{theorem}
\begin{proof}
    Suppose the covering is normal, let $g^{-1}Hg$ be a conjugate of $H$ in $\pi_1(X,x_0)$. Then, there is correspondingly $\wt x_1\in p^{-1}(x_0)$ such that $p_*(\pi_1(\wt X,\wt x_1)) = g^{-1}Hg$. Since the covering is normal, there is a deck transformation $f:\wt X\to\wt X$ taking $\wt x_0$ to $\wt x_1$. From \thref{thm:isomorphism-iff-image-equal}, we must have that $p_*(\pi_1(\wt X,\wt x_0)) = p_*(\pi_1(\wt X,\wt x_1))$, whereby $g^{-1}Hg = H$ and $H\unlhd\pi_1(X,x_0)$.

    Conversely, suppose $H\unlhd\pi_1(X,x_0)$ and let $\wt x_1\in p^{-1}(x_0)$. From \thref{thm:classification-covering-spaces}, we have that $p_*(\pi_1(\wt X,\wt x_1))$ is conjugate to $H$ but since $H$ is normal, the former is equal to $H$. As a result, from \thref{thm:isomorphism-iff-image-equal}, there is a deck transformation taking $x_0$ to $x_1$, consequently, the covering space is normal.

    Note that given $\wt x_0,\wt x_1\in p^{-1}(x_0)$, there is a unique deck transformation taking $\wt x_0$ to $\wt x_1$. Now, given some $[\gamma]\in N(H)$, there is a lift $\wt\gamma: I\to\wt X$ such that $\wt\gamma(0) = \wt x_0$. Define now the function $\phi: N(H)\to G(\wt X)$ by $\phi([\gamma]) = \wt\gamma(1)$. Let $[\gamma],[\delta]\in N(H)$ with $\sigma = \phi([\gamma])$ and $\tau = \phi([\delta])$. Then, it is not hard to see that $\gamma * \delta$ lifts to $\wt\gamma * \sigma(\wt\delta)$, which corresponds to the deck transformation $\sigma\circ\tau$, implying that $\phi$ is a homomorphism. Moreover, $\phi$ is also surjective, for if there is a deck transformation $\sigma$ taking $\wt x_0$ to $\wt x_1$, then $p_*(\pi_1(\wt X,\wt x_1)) = H$. Now, let $\wt\gamma$ be a path in $\wt X$ from $\wt x_0$ to $\wt x_1$ with $\gamma = p\circ\wt\gamma$. This implies $[\gamma]\in N(H)$, consequently, $\phi([\gamma]]) = \sigma$.

    We now contend that $\ker\phi = H$. Obviously $H\subseteq\ker\phi$. On the other hand, if $[\gamma]\in\ker\phi$, then $\gamma$ lifts to a loop based at $\wt x_0$, whereby, $[\gamma]\in H$. The proof is finished by invoking the first isomorphism theorem.
\end{proof}

\subsection{Covering Space Actions}

\begin{definition}[Covering Space Action]
    A \textit{group action} of $G$ on a topological space $Y$ is a homomorphism $\varphi: G\to\Aut_{\catTop}(Y)$. A \textit{covering space action} is a group action of $G$ on $Y$ such that for each $y\in Y$, there is a neighborhood $U$ of $y$ such that for all $g_1,g_2\in G$, $g_1U\cap g_2U\ne\emptyset$, if and only if  $g_1 = g_2$.
\end{definition}

We may rephrase the definition of a covering space action as: 
\begin{quote}
    A \textit{covering space action} of $G$ on $Y$ is a group action such that for each $y\in Y$, there is a neighborhood $U$ of $y$ such that for all $g\in G$, $U\cap gU\ne\emptyset$ if and only if $g = 1_G$.
\end{quote}

% \begin{proposition}
%     The group action of the group of deck transformations, $G(\wt X)$, of a covering space $p:\wt X\to X$ is a covering space action.
% \end{proposition}
% \begin{proof}
%     \todo{deck transformations are covering space actions}
% \end{proof}

\begin{theorem}
    Let $G$ act on $Y$ through a covering space action.
    \begin{enumerate}[label=(\alph*)]
        \item The quotient map $p: Y\to Y/G$ given by $p(y) = Gy$ is a normal covering space.\footnote{Hence the nomenclature}.
        \item If $Y$ is path connected, then $G$ is the group of deck transformations of the covering space $p: Y\to Y/G$ 
        \item If $Y$ is \ul{path connected and locally path connected}, then $G\cong\pi_1(Y/G, Gy_0)/p_*(\pi_1(Y, y_0))$.
    \end{enumerate}
\end{theorem}
\begin{proof}
\begin{enumerate}[label=(\alph*)]
    \item Let $Gy\in Y/G$. Since $G$ acts through a covering space action, there is a neighborhood $U$ of $Y$ such that the collection $\{gU\mid g\in G\}$ is that of disjoint open sets. Obviously, $V = \bigsqcup_{g\in G}gU$ is a saturated open set, whereby, $p(V)$ is open in $Y/G$ and a neighborhood of $Gy$. We contend that the restriction $p: U\to p(V)$ is a homeomorphism. Indeed, if $W\subseteq U$ is open, then $p(W)\subseteq p(V)$ is open, since $p(W) = p\left(\bigsqcup_{g\in G}gW\right)$ and the term within the brackets is a saturated open set. This immediately implies that $p$ is a covering map.

    Furthermore, for any $g_1y,g_2y\in Gy$, there is the action $g_2g_1^{-1}$ taking $g_1y$ to $g_2y$ whereby, the covering space is normal.

    \item Obviously, each element of $G$ is a deck transformation. On the other hand, if $f: Y\to Y$ is a deck transformation, then for any $y\in Y$, $f(y)\in Gy$, whereby, there is $g\in G$ such that $g(y) = f(y)$. From \thref{prop:deck-action-free}, we have that $g=f$, implying the desired conclusion. 
    
    \item This follows from \thref{thm:ftgt-covering-spaces}.\qedhere
\end{enumerate}
\end{proof}

\begin{example}[Fundamental group of $S^1$]
    Let the additive group $\Z$ act on $\R$ by translations. Then, $\R/\Z$ is homeomorphic to the circle $S^1$. The action of $\Z$ is properly discontinuous and $\R$ is simply connected and thus 
    \begin{equation*}
        \Z\cong\pi_1(S^1, s_0)/p_\ast(\pi_1(\R, x_0))\cong\pi_1(S^1, s_0).
    \end{equation*}
\end{example}

\begin{remark}
    Similarly, one can obtain the fundamental group of the torus $S^1\times S^1$ by considering the additive action of $\Z\times\Z$ on $\bbC$ which is also properly discontinuous. Note that this also gives the torus the structure of a Riemann surface.
\end{remark}

\begin{example}[Fundamental group of $\RP^n$]
    Let $n\ge 2$. Consider the action of $\Z/2\Z$ on $S^n$ wherein the nontrivial action is given by $x\mapsto -x$. Obviously this is a covering space action, whereby 
    \begin{equation*}
        \Z/2\Z\cong\pi_1(\RP^n, x_0)/p_\ast(\pi_1(S^n, s_0))\cong\pi_1(\RP^n, x_0)
    \end{equation*}
    where $x_0$ is the orbit of $s_0$ and we're done.

    Now, consider the case $n = 1$. We know that $\RP^1$ is homeomorphic to the circle and thus has fundamental group isomorphic to $\Z$.
\end{example}