Consider the heat equation 

\begin{equation*}
    \begin{cases}
        \partial_t u - \Delta u = 0 & \text{ on } (0,\infty)\times\R^n\\
        u = u_0 & t = 0,~x\in\R^n.
    \end{cases}
\end{equation*}

Take the Fourier transform in the $x$-variable to get 
\begin{equation*}
    \partial_t\wh u(\xi, t) = -\left(\sum_{j = 1}^n\xi_j^2\right)\wh u(\xi, t).
\end{equation*}

This is an ordinary differential equation with solution 
\begin{equation*}
    \wh u(\xi, t) = A(\xi)\exp\left(-\|\xi\|^2 t\right)
\end{equation*}
with initial conditions $\wh u = \wh u_0$ for $t = 0$. This gives 
\begin{equation*}
    A(\xi) = \wh u_0(\xi).
\end{equation*}

Therefore, 
\begin{equation*}
    \wh u(\xi, t) = \wh u_0(\xi)\exp\left(-\|\xi\|^2t\right).
\end{equation*}

Being the product of two Fourier transforms, the inverse fourier transform of the above function is the convolution of the individual inverse fourier transforms. 

The Inverse Fourier Transform of the second term is what we have already calculated, 
\begin{equation*}
    K_t(x) = \frac{1}{(4\pi t)^{n/2}}\exp\left(-\frac{|x|^2}{4t}\right),
\end{equation*}
which is called the Heat Kernel.

Therefore, 
\begin{equation*}
    u(x, t) = u_0(x)\ast K_t(x).
\end{equation*}

That is, 
\begin{equation*}
    u(x, t) = \frac{1}{(4\pi t)^{n/2}}\int_{\R^n}\exp\left(-\frac{|x - y|^2}{4t}\right)u_0(y)~dy
\end{equation*}
for $t > 0$ and $x\in\R^n$.

\section*{Properties of the Heat Kernel}

\begin{enumerate}
    \item $K_t(x)$ is smooth on $(0, \infty)\times\R^n$.
    \item $K_t(x) > 0$ for all $(x,t)\in\R^n\times(0,\infty)$.
    \item $(\partial_t - \Delta)K_t = 0$ for all $(x,t)\in\R^n\times(0,\infty)$. Take this as an exercise.
    \item $\int_{\R^n} K_t(x)~dx = 1$ for all $t > 0$.
    \item For all $\delta > 0$, we have that 
    \begin{equation*}
        \lim_{t\to 0}\int_{|x|\ge\delta}K_t(x)~dx = 0.
    \end{equation*}
\end{enumerate}

\begin{theorem}
    Let $f\in C(\R^n)\cap L^\infty(\R^n)$. Then, 
    \begin{equation*}
        u(x, t) := K_t\ast f = \frac{1}{(4\pi t)^{n/2}}\int_{\R^n}\exp\left(-\frac{|x - y|^2}{4t}\right)f(y)~dy
    \end{equation*}
    satisfies the heat equation.
\end{theorem}
\begin{proof}
    It is easy to see that $u$ satisfies the differential equation. It remains to show continuity. Indeed, 
    \begin{equation*}
        u(x, t) - f(x) = \int_{\R^n} K_t(x - y)\left(f(y) - f(x)\right)~dy.
    \end{equation*}
    Pick $\varepsilon > 0$. There is a $\delta > 0$ such that $|f(y) - f(x)| < \varepsilon$ whenever $|x - y| < \delta$. Then, we have 
    \begin{equation*}
        |u(x, t) - f(x)|\le\int_{|x - y| < \delta} + \int_{|x - y|\ge\delta}.
    \end{equation*}
    The first quantity is bounded above by $\varepsilon$ while the second tends to $0$ as $t\to\infty$. Conclude.
\end{proof}