Recall on $\R^n$, we have Green's Functions

\begin{equation*}
    G(x) = 
    \begin{cases}
        -\frac{1}{2\pi}\log|x| & n = 2\\
        \frac{1}{(n - 2)\omega_{n - 1}}\frac{1}{|x|^{n - 2}} & n\ge 3.
    \end{cases}
\end{equation*}
Then, $u(x) = (G\ast f)(x)$.

A harmonic function satisfies $\Delta u = 0$. Multiply by $u$ and integrate by parts to obtain 

\begin{equation*}
    0 = \int_{\R^n} u\Delta u = \sum_{i = 1}^n\int_{\R^n}u\partial_{ii}u.
\end{equation*}

This gives (check this!)
\begin{equation*}
    \int_{\R^n} |\nabla u|^2 = 0.
\end{equation*}
This shows that $u$ must be constant.

Let $E(u) = \int_{\R^n}|\nabla u|^2$. Consider 

\begin{equation*}
    \begin{cases}
        -\Delta u = 0 & \text{in } B(0, 1)\\
        u = 0 & \text{on }\partial B(0, 1).
    \end{cases}
\end{equation*}

Solutions of this equation can be obtained as 
\begin{equation*}
    \min_{u\in C^2(B(0, 1))}\int_{B(0, 1)}|\nabla u|^2.
\end{equation*}

Let $E(u)$ denote the functional $\int_{B(0, 1)}|\nabla u|^2$. Consider a minimizing sequence $(u_\alpha)$.

The Sobolev space $W^{1,2}$ is given by the set of all $u$ that satisfy 
\begin{equation*}
    \int_{B(0,1)}|\nabla u|^2 + u^2 < \infty.
\end{equation*}
which is equivalent to stating (using the Poincare inequality),
\begin{equation*}
    \int_{B(0,1)}|\nabla u|^2
\end{equation*}

Then, $u_\alpha$ weakly converges to $u_0$ in $W^{1,2}(B(0, 1))$ and $u_0$ solves the equation. In this case it is just the trivial solution but this gives a general method to find solutions to such initial value problems. This is called the Dirichlet principle.

\section*{Wave Equation}

\begin{equation*}
    \begin{cases}
    \partial_{tt} u = \Delta u & x\in\R^n,~t > 0\\
    u(x, 0) = f(x)\\
    \partial_t u(x, 0) = g(x).
    \end{cases}
\end{equation*}

Take fourier transform with respect to $x$ to obtain 
\begin{equation*}
    \partial_{tt}\wh u(\xi, t) + |\xi|^2\wh u(\xi, t) = 0.
\end{equation*}

The initial conditions become 
\begin{equation*}
    \wh u(\xi, 0) = \wh f(\xi)\qquad\partial_t\wh u(\xi, 0) = \wh g(\xi).
\end{equation*}

We get 
\begin{equation*}
    \wh u(\xi, t) = \wh f(\xi)\cos(|\xi|t) + \frac{\wh g(\xi)}{|\xi|}\sin(|\xi|t).
\end{equation*}

Now, take the Inverse Fourier transform and obtain the following 
\begin{equation*}
    u(x, t) = \frac{1}{(2\pi)^{n/2}}\int_{\R^n} e^{i\langle x,\xi\rangle}\cos(|\xi|t)\wh f(\xi)~d\xi + \frac{1}{(2\pi)^{n/2}}\int_{\R^n}e^{i\langle x,\xi\rangle}\sin(|\xi|t)\frac{\wh g(\xi)}{|\xi|}~d\xi.
\end{equation*}

Now write this as a convolution of the inverse fourier transforms of $\sin/x$ and $\cos$ respectively. This should give you the kernel corresponding to the wave equation. This is not beautiful.

Define 
\begin{equation*}
    E(t) = \int_{\R^n}\partial_t(u)^2 + \int_{\R^n} |\nabla u(t, \cdot)|^2.
\end{equation*}

Then, 
\begin{equation*}
    E'(t) = 0\implies E(t) = E(0) = \int_{\R^n} f^2 + \int_{\R^n} g^2.
\end{equation*}
that is, energy is conserved for the wave equation.

For $n = 1$, we have 
\begin{equation*}
    u(x,t) = \frac{f(x + t) + f(x - t)}{2} + \frac{1}{2}\int_{x - t}^{x + t}g(s)~ds.
\end{equation*}

For $n = 3$, 

\begin{equation*}
    u(x,T) = \partial_t\left(\frac{t}{4\pi}\int_{S^2}f(x - t\sigma)~d\sigma\right) + \frac{t}{4\pi}\int_{S^2}g(x - t\sigma)~d\sigma.
\end{equation*}

For $n = 2$, we have 
\begin{equation*}
    u(x, t) = \partial_t\left(\frac{t}{4\pi}\int_{|z|\le 1} f(x - tz)\frac{1}{\sqrt{1 - |z|^2}}~dz\right) + \frac{t}{4\pi}\int_{|z|\le 1}g(x - tz)\frac{1}{\sqrt{1 - |z|^2}}~dz.
\end{equation*}